GSE158422: Package Development

### 2023-12-21 figs/GSE158422_pkgdev.Rmd
update
remove stuff

@@

@@

@@

@@

head(myann)
table(anno$UCSC_RefGene_Group)
table(unlist(strsplit(myann$UCSC_RefGene_Group,";")))

>>>>

Source code: https://github.com/markziemann/gmea/blob/main/figs/GSE158422_pkgdev.Rmd

@@

Load packages.

@@

Updating gene names using the HGNC package because a lot of them have been updated over time.

@@

Here we conduct a differential analysis using limma.

@@

head(myann)
table(unlist(strsplit(myann$UCSC_RefGene_Group,";")))
